Import Data¶

The data set used for this practice and learning is House Sales Price on https://www.kaggle.com/c/house-prices-advanced-regression-techniques/data

```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
df = read.csv('D:/reza/dbimbing DATA SCIENCE/Code/train.csv')
head(df)
```

```{r}
missing.values <- df %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing==T) %>%
    select(-is.missing) %>%
    arrange(desc(num.missing)) 
```
```{r}
options(repr.plot.width = 10, repr.plot.height = 7)
missing.values %>%
    ggplot() +
    geom_bar(aes(x=key, y=num.missing), stat = 'identity') +
    labs(x='variable', y="number of missing values", title='Number of missing values') +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


Initial EDA

```{r}
glimpse(df)
```
this is the first initial EDA :

    there's 1,460 rows of data with 81 columns
    data consist of only String and Integer values
    with the target of variable is SalePrice which are the dependent variable



1. Start with the target SalePrice

```{r}
df$SalePrice %>% summary()
```


    the mean sale is on 180k
    the highest sale on 755k
    the cheapest sale on 34k
    not normally distribute

```{r}
options(repr.plot.width = 10, repr.plot.height = 7)
df %>%
    ggplot(aes(x=SalePrice))+
    geom_histogram(bins = 30)
```

is a positive skew distribution

```{r}
  df %>%
    ggplot(aes(x=SalePrice))+
    geom_boxplot()
```

there's an outlier on the data , with 2 outlier that beyond than the other

```{r}
df %>%
  ggplot(aes(x = SalePrice)) +
  geom_histogram(aes(fill = factor(YrSold)), alpha = 0.5)
```

before move'on on to the next, i want to know the House SalePrice Through the years and as i can see, the house sales at the peak at 2006 and slightly slope over the years until 2010. it is because Financial Crisis that start on 2007



2. Correlations

```{r fig.width=15, fig.height=10, echo=FALSE}
df %>% select(-Id,-LotFrontage,-MasVnrArea,-GarageYrBlt) %>%
  select_if(is.numeric) %>% cor() %>% corrplot::corrplot(type='lower',method = 'number')
```
from the heat map above , we clearly can see that there's 5 variable that had a strong correlation with the variable target :

    OveraalQuall = 0.79
    GrLivArea = 0.71
    GarageCars = 0.64
    GarageArea = 0.62
    1stFlrSF = 0.61

from this variable shows has effect for the SalePrice, such as the quality, house area as well as other



3. Relationship target Variable


as you know if the quality is low so the price is, and vice versa, oke than lets see whats the visual show us The corresponding variable is OverallQual which values consist of :

    10 = Very Excellent
    9 = Excellent
    8 = Very Good
    7 = Good
    6= = Average
    5 = Average
    4 = Below Average
    3 = Fair
    2 = Poor
    1 = Very Poor
```{r}
df %>% 
ggplot(aes(x=factor(OverallQual),y=SalePrice)) + geom_boxplot()
```

    
```{r}
df %>%
  ggplot(aes(x = GrLivArea, y = SalePrice)) +
  geom_smooth(method='lm', se=FALSE)+
  labs(title = 'Sales price', subtitle = 'directly proportional as bigger area more pricey \n')+
  geom_point()
```
```{r}
df %>%
  ggplot(aes(x = GarageCars, y = SalePrice)) +
  geom_smooth(method='lm', se=FALSE)+
  geom_point()
```
    
```{r}
df %>%
  ggplot(aes(x = GarageArea, y = SalePrice)) +
  geom_smooth(method='lm', se=FALSE)+
  geom_point()
```

```{r}
df %>%
  ggplot(aes(x = X1stFlrSF, y = SalePrice)) +
  geom_smooth(method='lm', se=FALSE)+
  geom_point()
```
According to the heatmap there are the graph SalePrice with several strong correlation

    1. bassicly the graph say the truth the higher the quality, more pricey it is
    2. in this graph GrlivArea there 2 anomalies/outlier. with the house area more than 4k square feet but it sales under 200k , what        happend? is there any particular reason the owner sell it under the market ?
    3. For the GarageCars and GarageArea its just the same like a twin.
    4. and 1stFlrSF slightly same with the GrlivArea



4. Feature Engineering
```{r}
  df2 = df %>% 
  mutate(age_after_remodAdd = 2021 - YearRemodAdd,                            
         age_built_to_remodAdd = YearRemodAdd - YearBuilt,                    
         age_sell = YrSold - YearBuilt,                                        
         age_sell_to_month = age_sell * 12,                                  
         OQ_redefine = case_when(OverallQual <= 4 ~ "low",                     
                        OverallQual > 4 & OverallQual < 8  ~ "medium", 
                        OverallQual >= 8 ~ "high"),
         MS_redefine = case_when(MoSold <= 6 ~ "Awal Tahun",                   
                        MoSold > 6 ~ "Akhir Tahun"),
         HouseType = case_when(YearBuilt >= 1800 & YearBuilt <= 1950 ~ "Antique", 
                     YearBuilt >= 1951 & YearBuilt <= 2007 ~ "Recent",
                     YearBuilt > 2008 ~ "Modern"),
         quartal = case_when(MoSold <= 3 ~ "Quartal 1",                  
                        MoSold > 3 & MoSold <= 6  ~ "Quartal 2",
                        MoSold > 6 & MoSold <= 9  ~ "Quartal 3",
                        MoSold > 9 ~ "Quartal 4"))
```
Make a new columns usia_after_remodAdd, usia_built_to_remodAdd, usia_jual, usia_jual_to_month, OQ_redefine, MS_redefine, HouseType, quartal

```{r}
df2 %>% 
  select(Id, age_after_remodAdd, age_built_to_remodAdd, age_sell, age_sell_to_month, OQ_redefine, MS_redefine, HouseType, quartal)
  head(df2)
```


